---
title: "Evaluating GPP predictions"
author: "Pepa Arán"
date: "2023-11-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(patchwork)
library(ggrepel)
library(yardstick)
# library(rbeni)    # get it by devtools::install_github("https://github.com/stineb/rbeni.git")
library(cowplot)
# library(jcolors)
# library(ingestr)
library(khroma)
library(ggplot2)

source(here::here("R/rolling_rsq.R"))
source(here::here("R/rolling_rmse.R"))
```

## Read in model predictions

```{r}
# Leave-site-out predictions from LSTM model without categorical covariates
lstm_lso <- read_csv(here::here("models/preds/lstm_lso_epochs_150_patience_20_hdim_256_conditional_0.csv"))

# Leave-site-out predictions from LSTM model without wscal
lstm_wscal_lso <- read_csv(here::here("models/preds/lstm_lso_epochs_150_patience_20_hdim_256_conditional_0_no_wscal.csv"))

# Leave-site-out predictions from LSTM model with less parameters
lstm_lso_128 <- read_csv(here::here("models/preds/lstm_lso_epochs_150_patience_20_hdim_128_conditional_0.csv"))

# Leave-site-out predictions from DNN
dnn_lso <- read_csv(here::here("models/preds/dnn_lso_epochs_150_patience_20.csv"))

# Leave-site-out predictions from DNN without wscal
dnn_wscal_lso <- read_csv(here::here("models/preds/dnn_lso_epochs_150_patience_20_no_wscal.csv"))

# Leave-vegetation-out predictions from LSTM


# Leave-continent-out predictions from LSTM


# P-model simulations
pmodel <- read_csv(here::here("data/external/pmodel_outputs.csv"))

# Input data frame containing sites metadata
df_metadata <- read_csv(here::here("data/processed/df_imputed.csv")) |>
  dplyr::group_by(sitename) |>
  dplyr::summarise(ai = first(ai),
                   koeppen_code = first(koeppen_code),
                   classid = first(classid)) |>
  # Add coordinates from another file
  dplyr::left_join(
    read_csv(here::here("data/external/fluxnet2015_sites_metainfo.csv")) |>
      dplyr::select(mysitename, lon, lat, elv),
    by = join_by( sitename == mysitename)
  )
```

## Evaluate LSOCV

```{r}
# Compute R2 (traditional and correlation definitions) and RMSE
# for all trained models
r2 <- lstm_lso |> 
  
  ## LSTM
  group_by(sitename) |> 
  nest() |> 
  mutate(out = purrr::map(data, ~rsq(., GPP_NT_VUT_REF, gpp_lstm, na_rm = TRUE)),
         out_trad = purrr::map(data, ~rsq_trad(., GPP_NT_VUT_REF, gpp_lstm, na_rm = TRUE)),
         out_rmse = purrr::map(data, ~rmse(., GPP_NT_VUT_REF, gpp_lstm, na_rm = TRUE))) |> 
  mutate(rsq_lstm = purrr::map_dbl(out, ~pull(., .estimate)),
         rsq_trad_lstm = purrr::map_dbl(out_trad, ~pull(., .estimate)),
         rmse_lstm = purrr::map_dbl(out_rmse, ~pull(., .estimate))) |> 
  dplyr::select(sitename, rsq_lstm, rsq_trad_lstm, rmse_lstm) |>
  dplyr::left_join(
    pmodel |>
      
      ## P-model
      group_by(sitename) |>
      nest() |>
      mutate(out = purrr::map(data, ~rsq(., gpp, mod, na_rm = TRUE)),
             out_trad = purrr::map(data, ~rsq_trad(., gpp, mod, na_rm = TRUE)),
             out_rmse = purrr::map(data, ~rmse(., gpp, mod, na_rm = TRUE))) |>
      mutate(rsq_pmodel = purrr::map_dbl(out, ~pull(., .estimate)),
             rsq_trad_pmodel = purrr::map_dbl(out_trad, ~pull(., .estimate)),
             rmse_pmodel = purrr::map_dbl(out_rmse, ~pull(., .estimate))) |>
      select(sitename, rsq_pmodel, rsq_trad_pmodel, rmse_pmodel),
    by = 'sitename'
  ) |>
  dplyr::left_join(
    dnn_lso |> 
  
      ## DNN
      group_by(sitename) |> 
      nest() |> 
      mutate(out = purrr::map(data, ~rsq(., GPP_NT_VUT_REF, gpp_dnn, na_rm = TRUE)),
           out_trad = purrr::map(data, ~rsq_trad(., GPP_NT_VUT_REF, 
                                                 gpp_dnn, na_rm = TRUE)),
           out_rmse = purrr::map(data, ~rmse(., GPP_NT_VUT_REF, gpp_dnn, na_rm = TRUE))) |> 
    mutate(rsq_dnn = purrr::map_dbl(out, ~pull(., .estimate)),
           rsq_trad_dnn = purrr::map_dbl(out_trad, ~pull(., .estimate)),
           rmse_dnn = purrr::map_dbl(out_rmse, ~pull(., .estimate))) |> 
    dplyr::select(sitename, rsq_dnn, rsq_trad_dnn, rmse_dnn),
  by = 'sitename'
  ) |>
  dplyr::left_join(
    lstm_lso_128 |> 
  
      ## LSTM - smaller hidden dimension
      group_by(sitename) |> 
      nest() |> 
      mutate(out = purrr::map(data, ~rsq(., GPP_NT_VUT_REF, gpp_lstm, na_rm = TRUE)),
           out_trad = purrr::map(data, ~rsq_trad(., GPP_NT_VUT_REF, 
                                                 gpp_lstm, na_rm = TRUE))) |> 
    mutate(rsq_lstm_128 = purrr::map_dbl(out, ~pull(., .estimate)),
           rsq_trad_lstm_128 = purrr::map_dbl(out_trad, ~pull(., .estimate))) |> 
    dplyr::select(sitename, rsq_lstm_128, rsq_trad_lstm_128),
  by = 'sitename'
  ) |>
  dplyr::left_join(
    df_metadata |>
      dplyr::select(sitename, ai, classid, koeppen_code),
    by = 'sitename'
  )
```

We start by visually comparing the performance of the neural networks against the P-model, and then against each other.
```{r}
# Compare LSTM and DNN to P-model
par(mfrow=c(2,2))
plot(rsq_trad_lstm ~ rsq_trad_pmodel, data = r2, main = "LSTM, Traditional R2")
abline(a=0, b=1, lty=2)

plot(rsq_trad_dnn ~ rsq_trad_pmodel, data = r2, main = "DNN, Traditional R2")
abline(a=0, b=1, lty=2)

plot(rsq_lstm ~ rsq_pmodel, data = r2, ylim = c(0,1), xlim = c(0,1),
     main = "LSTM, correlation R2")
abline(a=0, b=1, lty=2)

plot(rsq_dnn ~ rsq_pmodel, data = r2,  ylim = c(0,1), xlim = c(0,1),
     main = "DNN, correlation R2")
abline(a=0, b=1, lty=2)

# Compare LSTM to DNN
plot1 <- ggplot(r2) +
  geom_point(aes(x=rsq_trad_dnn, y=rsq_trad_lstm),
             color="red") +
  geom_abline(slope=1, intercept=0, lty=2) +
  xlab("DNN") + ylab("LSTM") +
  labs(title = "Traditional R2")

plot2 <- ggplot(r2) +
  geom_point(aes(x=rsq_dnn, y=rsq_lstm),
             color="red") +
  geom_abline(slope=1, intercept=0, lty=2) +
  xlab("DNN") + ylab("LSTM") +
  labs(title = "Correlation R2")

plot3 <- ggplot(r2) +
  geom_point(aes(x=rmse_dnn, y=rmse_lstm),
             color="red") +
  geom_abline(slope=1, intercept=0, lty=2) +
  xlab("DNN") + ylab("LSTM") +
  labs(title = "RMSE")

cowplot::plot_grid(plot1, plot2, plot3)
```

After the visualisation, let's perform a comparing means test between the LSTM and DNN metrics,
in order to check whether there is a significant improvement in performance.
```{r}
# First, test normality assumption
shapiro.test(r2$rsq_lstm)
shapiro.test(r2$rsq_dnn)
shapiro.test(r2$rsq_trad_lstm)
shapiro.test(r2$rsq_trad_dnn)

# All tests are rejected with a very low p.value, so these data are not 
# normally distributed

# Perform (non-parametric) Wilcoxon rank test, because the t.test normality 
# assumption does not hold. Since the performance should be compared for each
# site, we use a paired test
wilcox.test(x = r2$rsq_lstm, y = r2$rsq_dnn, paired = TRUE,
            alternative = "greater")     # H0: x <= y   vs   H1: x > y
# Null hypothesis accepted. No significant improvement

wilcox.test(x = r2$rsq_trad_lstm, y = r2$rsq_trad_dnn, paired = TRUE,
            alternative = "greater")     # H0: x <= y   vs   H1: x > y
# Null hypothesis accepted. No significant improvement
```

### Paper figures

Patterns of the seasonal GPP predictions, by climate zone.
```{r}
df_season_kgclimate <- lstm_lso |>
  # Join LSTM and DNN predictions
  left_join(
    dnn_lso,
    by = c('sitename', 'date', 'GPP_NT_VUT_REF')) |>
  # Join P-model predictions
  left_join(
    pmodel,
    by = c('sitename', 'date')
  ) |>
  rename(obs = GPP_NT_VUT_REF,
         lstm = gpp_lstm,
         dnn = gpp_dnn,
         pmodel = mod)  |> 
  # Join site metadata
  left_join(
    df_metadata,
    by = "sitename"
  ) |>
  # Get day of year
  mutate(doy = lubridate::yday(date),
         northsouth = ifelse(lat>0, "North", "South")) |> 
  # Remove unknown climates
  dplyr::filter(koeppen_code != "-") |>
  # Separate into northern and southern hemisphere for seasonal comparison
  mutate(kg_code_northsouth = paste(koeppen_code, northsouth)) |> 
  # Aggregate dates over day of year, taking mean over several years for each site
  group_by(kg_code_northsouth, doy) |> 
  summarise(obs = mean(obs, na.rm = TRUE), 
            lstm = mean(lstm, na.rm = TRUE), 
            dnn = mean(dnn, na.rm = TRUE),
            pmodel = mean(pmodel, na.rm = TRUE))

df_season_kgclimate |> 
  pivot_longer(c(obs, lstm, dnn), names_to = "Source", values_to = "gpp") |> 
  ggplot(aes(doy, gpp, color = Source)) +
  geom_line() +
  scale_color_manual(values = c("dnn" = "royalblue", "lstm" = "red", "obs" = "black"), labels = c("DNN", "LSTM", "obs.")) +
  labs(y = expression( paste("GPP (g C m"^-2, " d"^-1, ")" ) ),
       x = "Day of year") +
  facet_wrap(~kg_code_northsouth)

# Save figure as pdf for manuscript
# ggsave("fig/meanseasonalcycle_by_climate.pdf", width = 9, height = 6)
```


Patterns of R2 with respect to the aridity index, vegetation types and climate class.
````{r}
# LSTM - AI
gg1 <- r2 |> 
  ggplot(aes(x = ai, y = rsq_lstm, color = classid, label = sitename)) +
  geom_point(size = 2) +
  theme_classic() +
  labs(x = "P/PET", y = expression(paste(italic(R)^2))) +
  khroma::scale_color_discreterainbow(name = "") +
  geom_text_repel(min.segment.length = 0,
                  segment.size = 0.2,
                  size = 2,
                  seed = 42,
                  box.padding = 0.5,
                  color = "grey50")

# LSTM - veg type
gg2 <- r2 |> 
  ggplot(aes(x = reorder(classid, rsq_lstm), y = rsq_lstm)) +
  geom_boxplot(fill = "azure3", outlier.shape = NA) +
  geom_jitter(width = 0.25, color = "grey50") +
  theme_classic() +
  labs(x = "Vegetation type", y = expression(paste(italic(R)^2)))

# LSTM - koeppen climate
gg3 <- r2 |> 
  drop_na(koeppen_code) |> 
  filter(koeppen_code != "-") |> 
  ggplot(aes(x = reorder(koeppen_code, rsq_lstm), y = rsq_lstm)) +
  geom_boxplot(fill = "azure3", outlier.shape = NA) +
  geom_jitter(width = 0.25, color = "grey50") +
  theme_classic() +
  labs(x = "Koeppen-Geiger climate class", y = expression(paste(italic(R)^2)))

leftpanel <- cowplot::plot_grid(gg2, gg3, labels = c("b", "c"), ncol = 1)

cowplot::plot_grid(gg1, leftpanel,
                   rel_widths = c(1.2, 1), 
                   labels = c("a", ""), 
                   ncol = 2)
```

Now, we produce the same figures with the traditional R2.
````{r}
# LSTM - AI
gg1 <- r2 |> 
  ggplot(aes(x = ai, y = rsq_trad_lstm, color = classid, label = sitename)) +
  geom_point(size = 2) +
  theme_classic() +
  labs(x = "P/PET", y = expression(paste(italic(R)^2))) +
  khroma::scale_color_discreterainbow(name = "") +
  geom_text_repel(min.segment.length = 0,
                  segment.size = 0.2,
                  width = 0.1,
                  size = 2,
                  seed = 42,
                  box.padding = 0.5,
                  color = "grey50")

# LSTM - veg type
gg2 <- r2 |> 
  ggplot(aes(x = reorder(classid, rsq_trad_lstm), y = rsq_trad_lstm)) +
  geom_boxplot(fill = "azure3", outlier.shape = NA) +
  geom_jitter(width = 0.25, color = "grey50") +
  theme_classic() +
  labs(x = "Vegetation type", y = expression(paste(italic(R)^2)))

# LSTM - koeppen climate
gg3 <- r2 |> 
  drop_na(koeppen_code) |> 
  filter(koeppen_code != "-") |> 
  ggplot(aes(x = reorder(koeppen_code, rsq_trad_lstm), y = rsq_trad_lstm)) +
  geom_boxplot(fill = "azure3", outlier.shape = NA) +
  geom_jitter(width = 0.25, color = "grey50") +
  theme_classic() +
  labs(x = "Koeppen-Geiger climate class", y = expression(paste(italic(R)^2)))

leftpanel <- cowplot::plot_grid(gg2, gg3, labels = c("b", "c"), ncol = 1)

cowplot::plot_grid(gg1, leftpanel,
                   rel_widths = c(1.2, 1), 
                   labels = c("a", ""), 
                   ncol = 2
                   )
```

## Comparison of LSTM and DNN with rolling R2 values

```{r}
# Get the length of time series, since the longest records of data
# will show learning the best (supposedly)
ts_sites <- lstm_lso |>
  group_by(sitename) |>
  summarise(n_days = n()) |>
  arrange(desc(n_days))

ts_sites
```

```{r}

site <- 'US-Ha1'    # change site name to observe difference
window <- 365

# Compute rolling R2 for the LSTM and DNN results
r2_rolling <- data.frame(
  lstm = lstm_lso |>
    filter(sitename == site) |>
    rolling_rsq(truth = 'GPP_NT_VUT_REF', estimate = "gpp_lstm"),
  dnn = dnn_lso |>
    filter(sitename == site) |>
    rolling_rsq(truth = 'GPP_NT_VUT_REF', estimate = 'gpp_dnn')
)

r2_rolling <- cbind(r2_rolling, 
                    lstm_lso |>
                      filter(sitename == site) |>
                      select(date) |>
                      slice_tail(n = nrow(r2_rolling)))

ggplot(data = r2_rolling |>
         tidyr::pivot_longer(cols=c(lstm, dnn))) +
  geom_line(aes(y=value, color=name, x=date)) +
  labs(title = paste(site, "  rsq_lstm =", r2[r2$sitename == site, 'rsq_lstm'] |>
                       round(3),
                     "  rsq_dnn =", r2[r2$sitename == site, 'rsq_dnn'] |>
                       round(3)))


```

Implement the rolling R2 calculation, for all sites and the main LSTM and DNN models.
```{r, eval = FALSE, warning=FALSE}
# Get LSTM and DNN rolling R2 scores
sites <- df_metadata$sitename
n_sites <- length(sites)

# Set window to compute rolling R2
window <- 365

# Initialize object with results for first site
rolling_r2_sites <- data.frame(
  sitename = sites[1],
  lstm = lstm_lso |>
    filter(sitename == sites[1]) |>
    rolling_rsq(truth = 'GPP_NT_VUT_REF', estimate = "gpp_lstm"),
  dnn = dnn_lso |>
    filter(sitename == sites[1]) |>
    rolling_rsq(truth = 'GPP_NT_VUT_REF', estimate = 'gpp_dnn'))

rolling_r2_sites <- cbind(rolling_r2_sites,
                          lstm_lso |>
                            filter(sitename == sites[1]) |>
                            select(date) |>
                            slice_tail(n = nrow(rolling_r2_sites)))

# Continue computing results for other sites
for(site in sites[-1]){
  print(paste("Computing rolling mean for:", site))
  
    r2_rolling <- data.frame(
      sitename = site,
      lstm = lstm_lso |>
        filter(sitename == site) |>
        rolling_rsq(truth = 'GPP_NT_VUT_REF', estimate = "gpp_lstm"),
      dnn = dnn_lso |>
        filter(sitename == site) |>
        rolling_rsq(truth = 'GPP_NT_VUT_REF', estimate = 'gpp_dnn')
    )
    
    r2_rolling <- cbind(r2_rolling, 
                        lstm_lso |>
                          filter(sitename == site) |>
                          select(date) |>
                          slice_tail(n = nrow(r2_rolling)))
    
  # Append to results from other sites
  rolling_r2_sites <- rbind(rolling_r2_sites,
                            r2_rolling)
}

# Write results, because they take long to compute
saveRDS(rolling_r2_sites, file = here::here("notebooks/rolling_r2_sites.rda"))
# saveRDS(rolling_r2_sites, file = here::here("notebooks/rolling_r2_sites_wscal.rda"))
```

```{r, echo = FALSE}
# Read in rolling R2 values if they've been read already
rolling_r2_sites <- readRDS(file = here::here("notebooks/rolling_r2_sites.rda"))
```

Aggregate the evolution of the R2 over all sites, for the same day (counting from the start of measurements).
```{r, eval = FALSE}
grouped <- rolling_r2_sites |>
          select(sitename, lstm, dnn) |>
          group_by(sitename)

# Aggregate the R2 scores, for the same "day since start of measurements"
rolling_r2_aggregated <- lapply(1:(ts_sites$n_days[1] - window),     # length of the longest time series
       function(i){ summarise(grouped, lstm = nth(lstm, i),
                              dnn = nth(dnn, i)) |>
           select(lstm, dnn) |> 
           apply(MARGIN = 2, FUN = mean, na.rm = TRUE)}) |>
  bind_rows() 

# Save aggregated values, it takes long to compute
# saveRDS(rolling_r2_aggregated, file = here::here("notebooks/rolling_r2_aggregated.rda"))
saveRDS(rolling_r2_aggregated, file = here::here("notebooks/rolling_r2_aggregated_wscal.rda"))
```

```{r, echo = FALSE}
# Change filename if you want to observe other results that have been already computed
rolling_r2_aggregated <- readRDS(file = here::here("notebooks/rolling_r2_aggregated.rda"))
```

```{r}
# Set window used to compute rolling R2
window <- 365

rolling_r2_aggregated |>
  mutate(id = row_number() + 365) |>
  pivot_longer(cols = c(lstm, dnn)) |>
  ggplot() +
  geom_line(aes(y=value, color=name, x=id)) +
  labs(title = "Rolling R2 score, averaged over all sites (without wscal)") +
  xlab("Day since first measurement") +
  ylab("R2")

```

Plot how many sites are used to computed the aggregated R2 above:
```{r}
data.frame(x = 365:ts_sites$n_days[1], y = sapply(365:ts_sites$n_days[1], function(x){
    ts_sites |>
        mutate(n = n_days > x) |>
        select(n) |>
        sum()
})) |>
  ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab("Length of time series") +
  ylab("Number of sites available") +
  labs(title = "Number of sites used to aggregate the rolling R2")

```

Plotting a few sites.
```{r}
rolling_r2_sites |>
  filter(sitename %in% c('US-Ha1', ''))
  pivot_longer(cols = c(lstm, dnn)) |>
  ggplot() +
  geom_line(aes(y=value, color=name, x=date)) +
  labs(title = paste(site, "  rsq_lstm =", r2[r2$sitename == site, 'rsq_lstm'] |>
                       round(3),
                     "  rsq_dnn =", r2[r2$sitename == site, 'rsq_dnn'] |>
                       round(3))) +
  facet_wrap( ~ sitename)

```

### Rolling R2 aggregated over vegetation types

```{r, message = FALSE}
window = 365

# Include site metadata
grouped <- rolling_r2_sites |>
  left_join(df_metadata,
            by = 'sitename') |>
  group_by(sitename, classid)

# Aggregate the R2 scores, for the same "day since start of measurements"
# and by vegetation type
rolling_r2_aggregated_classid <- lapply(1:(ts_sites$n_days[1] - window),     # length of the longest time series
       function(i){ summarise(grouped, 
                              lstm = nth(lstm, i),
                              dnn = nth(dnn, i)) |>
           group_by(classid) |>
           summarise(lstm = mean(lstm, na.rm = TRUE), 
                     dnn = mean(dnn, na.rm = TRUE)) |>
           ungroup() |>
           mutate(id = i)
         }) |>
  bind_rows() 
```

```{r}
# See number of sites per vegetation type
df_metadata |> 
  group_by(classid) |>
  summarise(n = n()) |>
  arrange(desc(n))

# Plot the aggregated results
rolling_r2_aggregated_classid |>
  pivot_longer(cols = c(lstm, dnn)) |>
  ggplot() +
  geom_line(aes(y=value, color=name, x=id)) +
  facet_wrap(~ classid) +
  labs(title = "Rolling R2 score, averaged over vegetation types (without wscal)") +
  xlab("Day since first measurement") +
  ylab("R2")
```

### Rolling R2 aggregate over climate zones

```{r message = FALSE}
# Repeat the exercise for Climate

grouped <- rolling_r2_sites |>
  left_join(df_metadata,
            by = 'sitename') |>
  group_by(sitename, koeppen_code)

# Aggregate the R2 scores, for the same "day since start of measurements"
# and by vegetation type
rolling_r2_aggregated_climate <- lapply(1:(ts_sites$n_days[1] - window),     # length of the longest time series
       function(i){ summarise(grouped, 
                              lstm = nth(lstm, i),
                              dnn = nth(dnn, i)) |>
           group_by(koeppen_code) |>
           summarise(lstm = mean(lstm, na.rm = TRUE), 
                     dnn = mean(dnn, na.rm = TRUE)) |>
           ungroup() |>
           mutate(id = i)
         }) |>
  bind_rows() 

# See number of sites per vegetation type
df_metadata |> 
  group_by(koeppen_code) |>
  summarise(n = n()) |>
  arrange(desc(n))

# Plot the aggregated results
rolling_r2_aggregated_climate |>
  pivot_longer(cols = c(lstm, dnn)) |>
  ggplot() +
  geom_line(aes(y=value, color=name, x=id)) +
  facet_wrap(~ koeppen_code) +
  labs(title = "Rolling R2 score, averaged over climate") +
  xlab("Day since first measurement") +
  ylab("R2")
```

## Rolling RMSE to evaluate model performance

```{r, eval = FALSE}
# Get LSTM and DNN rolling RMSE scores
sites <- df_metadata$sitename
n_sites <- length(sites)

# Set window to compute rolling R2
window <- 365

# Initialize object with results for first site
rolling_rmse_sites <- data.frame(
  sitename = sites[1],
  lstm = lstm_lso |>
    filter(sitename == sites[1]) |>
    rolling_rmse(truth = 'GPP_NT_VUT_REF', estimate = "gpp_lstm"),
  dnn = dnn_lso |>
    filter(sitename == sites[1]) |>
    rolling_rmse(truth = 'GPP_NT_VUT_REF', estimate = 'gpp_dnn'))

rolling_rmse_sites <- cbind(rolling_rmse_sites,
                          lstm_lso |>
                            filter(sitename == sites[1]) |>
                            select(date) |>
                            slice_tail(n = nrow(rolling_rmse_sites)))

# Continue computing results for other sites
for(site in sites[-1]){
  print(paste("Computing rolling mean for:", site))
  
    rmse_rolling <- data.frame(
      sitename = site,
      lstm = lstm_lso |>
        filter(sitename == site) |>
        rolling_rmse(truth = 'GPP_NT_VUT_REF', estimate = "gpp_lstm"),
      dnn = dnn_lso |>
        filter(sitename == site) |>
        rolling_rmse(truth = 'GPP_NT_VUT_REF', estimate = 'gpp_dnn')
    )
    
    rmse_rolling <- cbind(rmse_rolling, 
                        lstm_lso |>
                          filter(sitename == site) |>
                          select(date) |>
                          slice_tail(n = nrow(rmse_rolling)))
    
  # Append to results from other sites
  rolling_rmse_sites <- rbind(rolling_rmse_sites,
                            rmse_rolling)
}

# Write results, because they take long to compute. Read in later if wanted
# saveRDS(rolling_rmse_sites, file = here::here("notebooks/rolling_rmse_sites.rda"))
saveRDS(rolling_rmse_sites, file = here::here("notebooks/rolling_rmse_sites_wscal.rda"))
```

Aggregate the evolution of the R2 over all sites, for the same day (counting from the start of measurements).
```{r, eval = FALSE}
grouped <- rolling_rmse_sites |>
          select(sitename, lstm, dnn) |>
          group_by(sitename)

# Aggregate the RMSE scores, for the same "day since start of measurements"
rolling_rmse_aggregated <- lapply(1:(ts_sites$n_days[1] - window),     # length of the longest time series
       function(i){ summarise(grouped, lstm = nth(lstm, i),
                              dnn = nth(dnn, i)) |>
           select(lstm, dnn) |> 
           apply(MARGIN = 2, FUN = mean, na.rm = TRUE)}) |>
  bind_rows() 

# Save aggregated values, they take long to compute. Read in later if wanted
saveRDS(rolling_rmse_aggregated, file = here::here("notebooks/rolling_rmse_aggregated.rda"))
```

Create general plots, with aggregations over all sites.
```{r}
# Set window used to compute rolling R2
window <- 365

rolling_rmse_aggregated |>
  mutate(id = row_number() + window) |>
  pivot_longer(cols = c(lstm, dnn)) |>
  ggplot() +
  geom_line(aes(y=value, color=name, x=id)) +
  labs(title = "Rolling RMSE score, averaged over all sites (without wscal)") +
  xlab("Day since first measurement") +
  ylab("RMSE")


data.frame(x = window:ts_sites$n_days[1], y = sapply(window:ts_sites$n_days[1], function(x){
    ts_sites |>
        mutate(n = n_days > x) |>
        select(n) |>
        sum()
})) |>
  ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab("Length of time series") +
  ylab("Number of sites available") +
  labs(title = "Number of sites used to aggregate the rolling RMSE")

```

### Rolling RMSE aggregated over vegetation types

```{r, message = FALSE}
# Load results
rolling_rmse_sites <- readRDS(here::here("notebooks/rolling_rmse_sites.rda"))

window = 365

# Include site metadata
grouped <- rolling_rmse_sites |>
  left_join(df_metadata,
            by = 'sitename') |>
  group_by(sitename, classid)

# Aggregate the RMSE scores, for the same "day since start of measurements"
# and by vegetation type
rolling_rmse_aggregated_classid <- lapply(1:(ts_sites$n_days[1] - window),     # length of the longest time series
       function(i){ summarise(grouped, 
                              lstm = nth(lstm, i),
                              dnn = nth(dnn, i)) |>
           group_by(classid) |>
           summarise(lstm = mean(lstm, na.rm = TRUE), 
                     dnn = mean(dnn, na.rm = TRUE)) |>
           ungroup() |>
           mutate(id = i)
         }) |>
  bind_rows() 

# See number of sites per vegetation type
df_metadata |> 
  group_by(classid) |>
  summarise(n = n()) |>
  arrange(desc(n))

# Plot the aggregated results
rolling_rmse_aggregated_classid |>
  pivot_longer(cols = c(lstm, dnn)) |>
  ggplot() +
  geom_line(aes(y=value, color=name, x=id)) +
  facet_wrap(~ classid) +
  labs(title = "Rolling RMSE score, averaged over vegetation types (without wscal") +
  xlab("Day since first measurement") +
  ylab("RMSE")
```


